---
title: "E1 to E2"
author: ""
date: "April 30, 2021"
output: 
   html_document: 
     dev: png
     fig_height: 5
     fig_width: 5.5
     number_sections: yes
     toc: yes
     toc_depth: 4
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(knitr)
library(tidyverse)
library(dplyr)
library(tidyr)
library(tools)
library(ggplot2)
library(ARTool)
library(reshape2)
library(ez)
library(apa)
library(gridExtra)
library(phia)
library(viridis)
library(lsmeans)
library(gmodels)
library(DescTools)
library(MASS)
library(pander)
library(reticulate)
library(ggpubr)
library(xtable)
library(emmeans)
library(ggpattern)
library(car)
# Needed to correctly export fonts in pdf (may not be required)
library(extrafont)
options(ggpattern_use_R4.1_gradients = FALSE)
# Need to call extrafont::font_import() once in console and restart RStudio
```

```{r functions, echo=FALSE, warning=FALSE}

normalCheck = function(model) {
    res = residuals(model)
    qqnorm((res - mean(res)) / sd(res))
    abline(0, 1)
    print (shapiro.test(res))
}

normalize_condition <- function (column) {
  column %>% recode_factor(
    `pen,trackpad` = "trackpad,pen",
    `mouse,pen` = "mouse,pen",
    `pen,touch` = "pen,touch",
    `trackpad,touch` = "trackpad,touch",
    `mouse,trackpad` = "mouse,trackpad",
    `mouse,touch` = "mouse,touch"
  )
}

is_outlier <- function(column) {
  col_mean = mean(column)
  col_sd = sd(column)
  abs(column - col_mean) > 3 * col_sd
}
```


# Data Parsing

## Loading Data

```{r load, message=FALSE, warning=FALSE}
# Fetch the trial data.
data1.i <- read_csv(
  "data.csv",
  # I am using col_types to enforce the type of the data, and safely fail
  # if it changes unexpectedly. It isn't really required, but still good
  # practice.
  col_types = cols(
    participantNo = col_factor(),
    task = col_factor(),
    condition = col_factor(),
    forCond = col_factor(),
    mode = col_factor(),
    block = col_factor(),
    trialNo = col_double(),
    missCount = col_double(),
    dockingTime = col_double()
  )
) %>%
  # Normalize the condition values.
  mutate(condition = normalize_condition(condition),
         forCond = normalize_condition(forCond)) 
data1.i$methodSwitch = interaction(data1.i$mode, data1.i$condition)
data1.i$methodSwitch = as.factor(data1.i$methodSwitch)

data1.i.ms <- read_csv("data_ms.csv") %>% mutate(condition = normalize_condition(condition),
         forCond = normalize_condition(forCond))

# Fetch the trial data.
data2.i <- read_csv(
  "data_E2.csv",
  # I am using col_types to enforce the type of the data, and safely fail
  # if it changes unexpectedly. It isn't really required, but still good
  # practice.
  col_types = cols(
    participantNo = col_factor(),
    task = col_factor(),
    condition = col_factor(),
    forCond = col_factor(),
    mode = col_factor(),
    block = col_number(),
    trialNo = col_double(),
    missCount = col_double(),
    dockingTime = col_double()
  )
) %>%
  # Normalize the condition values.
  mutate(condition = normalize_condition(condition),
         forCond = normalize_condition(forCond)) 

data2.i$methodSwitch = interaction(data2.i$mode, data2.i$condition)
data2.i$methodSwitch = as.factor(data2.i$methodSwitch)

data2.i.ms <- read_csv("data_ms_E2.csv") %>% mutate(condition = normalize_condition(condition),
         forCond = normalize_condition(forCond))
data2.i.ms$block = as.numeric(data2.i.ms$block)
```

## Outlier Culling

### Switching Time Outliers

```{r}
data1 = data1.i %>% 
  group_by(task, condition) %>%
  filter(!is_outlier(dockingTime)) %>%
  ungroup()
data1$exp = "E1"

data1.ms = data1.i.ms %>% group_by(task, condition) %>%
  filter(!is_outlier(switchingTime)) %>%
  ungroup()
data1.ms$exp = "E1"

data2 = data2.i %>% 
  group_by(task, methodSwitch) %>%
  filter(!is_outlier(dockingTime)) %>%
  ungroup()
data2$exp = "E2"

data2.ms = data2.i.ms %>% group_by(task, condition) %>%
  filter(!is_outlier(switchingTime)) %>%
  ungroup()
data2.ms$exp = "E2"
```

## Data Aggregation

Removing Block  1 from mode switching trials - we consider these training blocks

```{r}
data1 = filter(data1, ((task == 'task' & block != 1) | task == 'baseline'))
data1.ms = filter(data1.ms, ((task == 'task' & block != 1) | task == 'baseline'))
data1.ms$block = as.factor(data1.ms$block)

data2 = filter(data2, ((task == 'task' & block > 1) | task == 'baseline'))
data2$block = as.factor(data2$block)
data2.ms = filter(data2.ms, ((task == 'task' & block > 1) | task == 'baseline'))
data2.ms$block = as.factor(data2.ms$block)

```

Get column names the same across E1 & E2
```{r}
data2 = dplyr::select(data2, -oldBlock)


data1.ms = dplyr::select(data1.ms, -c(msTimeA, msTimeC))
data2.ms = dplyr::select(data2.ms, -c(oldBlock, msToken, location))
```

Glue data frames together

```{r}
data.all = bind_rows(data1, data2)

data.ms.all = bind_rows(data1.ms, data2.ms)
```

Aggregating the cleaned data

```{r warning=FALSE, message=FALSE}
data.group =  summarize(group_by(data.all, participantNo, task, methodSwitch, condition, mode, block, exp), meanDockTime = mean(dockingTime), meanMisses = mean(missCount))
data.group$exp = as.factor(data.group$exp)

data.ms.all$condition = as.character(data.ms.all$condition)
data.ms.all$direction = ifelse(data.ms.all$cycleType == "A",
                                           paste(toTitleCase(sapply(
                                           strsplit(data.ms.all$condition, ","), "[", 1
                                           )), "to", toTitleCase(sapply(
                                           strsplit(data.ms.all$condition, ","), "[", 2
                                           ))),
                                           paste(toTitleCase(sapply(
                                           strsplit(data.ms.all$condition, ","), "[", 2
                                           )), "to", toTitleCase(sapply(
                                           strsplit(data.ms.all$condition, ","), "[", 1
                                           ))))
data.ms.all$condition = as.factor(data.ms.all$condition)
data.ms.all$block = as.factor(data.ms.all$block)
data.ms.all$participantNo = as.factor(data.ms.all$participantNo)
data.ms.all$direction = as.factor(data.ms.all$direction)
data.ms.all$exp = as.factor(data.ms.all$exp)

data.ms.dir =
  summarize(group_by(data.ms.all, participantNo, task, condition, direction, block, exp), meanSwitchTime = mean(switchingTime), meanMSTimeB = mean(msTimeB)) %>% filter(task == 'task')
```

```{r warning=FALSE, message=FALSE}
base = summarize(group_by(data.all, participantNo, task, condition, mode, block, exp), meanDockTime = mean(dockingTime), meanMisses = mean(missCount), meanWrong = mean(wrongModeCount), meanPos = mean(posMissCount))

mouse = filter(base, mode=='mouse')
touch = filter(base, mode=='touch')
pen = filter(base, mode=='pen')
trackpad = filter(base, mode=='trackpad')
```

## Mode Switching Task by Direction

### ANOVAs on ART Data

```{r warning=FALSE, message=FALSE}
a = art(meanMSTimeB ~ exp + Error(participantNo), data=filter(data.ms.dir, task == 'task'))
anova(a)
```

### Post-Hoc Comparisons

```{r warning=FALSE, message=FALSE}
b = art.con(a, "exp") %>% summary() %>% mutate(sig = ifelse(p.value < 0.05, "*", "")) 
b
c = as.data.frame(b) %>% mutate(sig = ifelse(p.value < 0.05, "*", "")) 
```

### Effect Sizes

```{r warning=FALSE, message=FALSE}
m.art.anova = anova(a)
m.art.anova$eta.sq.part = with(m.art.anova, `Sum Sq`/(`Sum Sq` + `Sum Sq.res`))
m.art.anova
```

## Docking Time

### ANOVAs on ART Data

```{r warning=FALSE, message=FALSE}
a = art(meanDockTime ~ exp + Error(participantNo), data=data.group)
anova(a)
```

### Post-Hoc Comparisons

```{r warning=FALSE, message=FALSE}
b = art.con(a, "exp") %>% summary() %>% mutate(sig = ifelse(p.value < 0.05, "*", "")) 
b
c = as.data.frame(b) %>% mutate(sig = ifelse(p.value < 0.05, "*", "")) 
```

### Effect Sizes

```{r warning=FALSE, message=FALSE}
m.art.anova = anova(a)
m.art.anova$eta.sq.part = with(m.art.anova, `Sum Sq`/(`Sum Sq` + `Sum Sq.res`))
m.art.anova
```

## Docking Misses

### ANOVAs on ART Data

```{r warning=FALSE, message=FALSE}
a = art(meanMisses ~ exp + Error(participantNo), data=data.group)
anova(a)
```

### Post-Hoc Comparisons

```{r warning=FALSE, message=FALSE}
b = art.con(a, "exp") %>% summary() %>% mutate(sig = ifelse(p.value < 0.05, "*", "")) 
b
c = as.data.frame(b) %>% mutate(sig = ifelse(p.value < 0.05, "*", "")) 
```

### Effect Sizes

```{r warning=FALSE, message=FALSE}
m.art.anova = anova(a)
m.art.anova$eta.sq.part = with(m.art.anova, `Sum Sq`/(`Sum Sq` + `Sum Sq.res`))
m.art.anova
```
