---
title: "Mode Switching Stats"
author: ""
date: "April 30, 2021"
output: 
   html_document: 
     dev: png
     fig_height: 6
     fig_width: 6.5
     number_sections: yes
     toc: yes
     toc_depth: 4
---

```{r setup, include=FALSE}
library(knitr)
library(dplyr)
library(tidyr)
library(tools)
library(ggplot2)
library(ARTool)
library(reshape2)
library(ez)
library(apa)
library(gmodels)
library(gridExtra)
library(MASS)
library(pander)
library(reticulate)
library(ggpubr)
library(xtable)
library(emmeans)
library(ggpattern)
library(tidyverse)
# Needed to correctly export fonts in pdf (may not be required)
library(extrafont)
# Need to call extrafont::font_import() once in console and restart RStudio
knitr::opts_chunk$set(echo = TRUE)
```

```{r functions, echo=FALSE, warning=FALSE}

normalCheck = function(model) {
    res = residuals(model)
    qqnorm((res - mean(res)) / sd(res))
    abline(0, 1)
    print (shapiro.test(res))
}

normalize_condition <- function (column) {
  column %>% recode_factor(
    `pen,trackpad` = "trackpad,pen",
    `mouse,pen` = "mouse,pen",
    `pen,touch` = "pen,touch",
    `trackpad,touch` = "trackpad,touch",
    `mouse,trackpad` = "mouse,trackpad",
    `mouse,touch` = "mouse,touch"
  )
}

is_outlier <- function(column) {
  col_mean = mean(column)
  col_sd = sd(column)
  abs(column - col_mean) > 3 * col_sd
}
```

# Data Parsing

## Loading Data

```{r message=FALSE, warning=FALSE}
# Fetch the trial data.
data.i <- read_csv(
  "data1.csv",
  # I am using col_types to enforce the type of the data, and safely fail
  # if it changes unexpectedly. It isn't really required, but still good
  # practice.
  col_types = cols(
    participantNo = col_factor(),
    task = col_factor(),
    condition = col_factor(),
    forCond = col_factor(),
    mode = col_factor(),
    block = col_number(),
    trialNo = col_double(),
    missCount = col_double(),
    dockingTime = col_double()
  )
) %>%
  # Normalize the condition values.
  mutate(condition = normalize_condition(condition),
         forCond = normalize_condition(forCond)) 

data.i$methodSwitch = interaction(data.i$mode, data.i$condition)
data.i$methodSwitch = as.factor(data.i$methodSwitch)

data.i.ms <- read_csv("data_ms.csv") %>% mutate(condition = normalize_condition(condition),
         forCond = normalize_condition(forCond))
data.i.ms$block = as.numeric(data.i.ms$block)
```

## Subtraction Times

**IMPORTANT** - you must run this block, then run the script "getMS.py" before proceeding.

```{r message=FALSE, include=FALSE}
sub_times = filter(data.i.ms, task=="baseline") %>%
  group_by(participantNo, mode, forCond) %>%
  summarize(mST = mean(switchingTime))

sub_times$forCond[sub_times$forCond == 'pen,trackpad'] = 'trackpad,pen'
sub_times$forCond[sub_times$forCond == 'pen,mouse'] = 'mouse,pen'
sub_times$forCond[sub_times$forCond == 'touch,pen'] = 'pen,touch'
sub_times$forCond[sub_times$forCond == 'touch,trackpad'] = 'trackpad,touch'
sub_times$forCond[sub_times$forCond == 'trackpad,mouse'] = 'mouse,trackpad'
sub_times$forCond[sub_times$forCond == 'touch,mouse'] = 'mouse,touch'

write.csv(sub_times, "subTimes.csv")
```


## Outlier Culling

### Switching Time Outliers

```{r}
data = data.i %>% 
  group_by(task, condition) %>%
  filter(!is_outlier(dockingTime)) %>%
  ungroup()
data.ms = data.i.ms %>% group_by(task, condition) %>%
  filter(!is_outlier(switchingTime)) %>%
  ungroup()
```

## Data Aggregation

Removing Blocks 1 & 2 from mode switching trials - we consider these training blocks

```{r}
data = filter(data, ((task == 'task' & block > 2) | task == 'baseline'))
data$block = as.factor(data$block)
data.ms = filter(data.ms, ((task == 'task' & block > 2) | task == 'baseline'))
data.ms$block = as.factor(data.ms$block)

```

Aggregating the cleaned data

```{r warning=FALSE, message=FALSE}
data.group =  summarize(group_by(data, participantNo, task, methodSwitch, condition, mode, block), meanDockTime = mean(dockingTime), meanMisses = mean(missCount)) %>% filter(task == 'task')


data.stats = data %>% 
  group_by(task, methodSwitch, condition, mode) %>%
  summarize(mDT = mean(dockingTime), cuDT = ci(dockingTime)[3], clDT = ci(dockingTime)[2], sdDT = sd(dockingTime),
            mMC = mean(missCount), cuMC = ci(missCount)[3], clMC = ci(missCount)[2], sdMC = sd(missCount))

data.stats.block = data %>% 
  group_by(task, methodSwitch, block) %>%
  summarize(mDT = mean(dockingTime), cuDT = ci(dockingTime)[3], clDT = ci(dockingTime)[2], sdDT = sd(dockingTime),
            mMC = mean(missCount), cuMC = ci(missCount)[3], clMC = ci(missCount)[2], sdMC = sd(missCount))

data.ms$condition = as.character(data.ms$condition)
data.ms$direction = ifelse(data.ms$cycleType == "A",
                                           paste(toTitleCase(sapply(
                                           strsplit(data.ms$condition, ","), "[", 1
                                           )), "to", toTitleCase(sapply(
                                           strsplit(data.ms$condition, ","), "[", 2
                                           ))),
                                           paste(toTitleCase(sapply(
                                           strsplit(data.ms$condition, ","), "[", 2
                                           )), "to", toTitleCase(sapply(
                                           strsplit(data.ms$condition, ","), "[", 1
                                           ))))
data.ms$condition = as.factor(data.ms$condition)
data.ms$block = as.factor(data.ms$block)
data.ms$participantNo = as.factor(data.ms$participantNo)
data.ms$direction = as.factor(data.ms$direction)
data.ms$location = as.factor(data.ms$location)

data.ms.group = summarize(group_by(data.ms, participantNo, task, condition, block), meanSwitchTime = mean(switchingTime), meanMSTimeB = mean(msTimeB)) %>% filter(task == 'task')

data.ms.dir =
  summarize(group_by(data.ms, participantNo, task, condition, direction, block), meanSwitchTime = mean(switchingTime), meanMSTimeB = mean(msTimeB)) %>% filter(task == 'task')

data.ms.loc =
  summarize(group_by(data.ms, participantNo, task, condition, location, block), meanSwitchTime = mean(switchingTime), meanMSTimeB = mean(msTimeB)) %>% filter(task == 'task')


data.ms.stats = data.ms %>% 
  group_by(task, condition) %>% 
  summarize(mST = mean(switchingTime), cuST = ci(switchingTime)[3], clST = ci(switchingTime)[2], sdST = sd(switchingTime),
            mMTB = mean(msTimeB), cuMTB = ci(msTimeB)[3], clMTB = ci(msTimeB)[2], sdMTB = sd(msTimeB)) %>% filter(task == 'task')

data.ms.stats.direction = data.ms %>% 
  group_by(task, condition, direction, cycleType) %>% 
  summarize(mST = mean(switchingTime), cuST = ci(switchingTime)[3], clST = ci(switchingTime)[2], sdST = sd(switchingTime),
            mMTB = mean(msTimeB), cuMTB = ci(msTimeB)[3], clMTB = ci(msTimeB)[2], sdMTB = sd(msTimeB)) %>% filter(task == 'task')

data.ms.stats.direction.block = data.ms %>% 
  group_by(task, condition, direction, cycleType, block) %>% 
  summarize(mST = mean(switchingTime), cuST = ci(switchingTime)[3], clST = ci(switchingTime)[2], sdST = sd(switchingTime),
            mMTB = mean(msTimeB), cuMTB = ci(msTimeB)[3], clMTB = ci(msTimeB)[2], sdMTB = sd(msTimeB)) %>% filter(task == 'task')

data.ms.stats.block = data.ms %>% 
  group_by(task, condition, block) %>% 
  summarize(mST = mean(switchingTime), cuST = ci(switchingTime)[3], clST = ci(switchingTime)[2], sdST = sd(switchingTime),
            mMTB = mean(msTimeB), cuMTB = ci(msTimeB)[3], clMTB = ci(msTimeB)[2], sdMTB = sd(msTimeB))%>% filter(task == 'task')

data.ms.stats.loc = data.ms %>% 
  group_by(task, condition, location) %>% 
  summarize(mST = mean(switchingTime), cuST = ci(switchingTime)[3], clST = ci(switchingTime)[2], sdST = sd(switchingTime),
            mMTB = mean(msTimeB), cuMTB = ci(msTimeB)[3], clMTB = ci(msTimeB)[2], sdMTB = sd(msTimeB))%>% filter(task == 'task')

data.ms.stats.loc2 = data.ms %>% 
  group_by(task,  location) %>% 
  summarize(mST = mean(switchingTime), cuST = ci(switchingTime)[3], clST = ci(switchingTime)[2], sdST = sd(switchingTime),
            mMTB = mean(msTimeB), cuMTB = ci(msTimeB)[3], clMTB = ci(msTimeB)[2], sdMTB = sd(msTimeB))%>% filter(task == 'task')



lvls = c("Pen to Touch", "Touch to Pen", "Pen to Mouse", "Mouse to Pen", "Mouse to Touch", "Touch to Mouse", "Trackpad to Mouse", "Mouse to Trackpad", "Pen to Trackpad", "Trackpad to Pen", "Trackpad to Touch", "Touch to Trackpad")
data.ms.stats.direction$direction = factor(data.ms.stats.direction$direction, levels=lvls)

```

```{r warning=FALSE, message=FALSE}
base = summarize(group_by(data, participantNo, task, condition, mode, block), meanDockTime = mean(dockingTime), meanMisses = mean(missCount), meanWrong = mean(wrongModeCount), meanPos = mean(posMissCount))

mouse = filter(base, mode=='mouse')
touch = filter(base, mode=='touch')
pen = filter(base, mode=='pen')
trackpad = filter(base, mode=='trackpad')
```

# Histograms

```{r warning=FALSE, message=FALSE, echo=FALSE}
# hist(data.i.ms$msTimeB)
# hist(data.ms$msTimeB)
# hist(data.ms.group$meanMSTimeB)
# hist(data.ms.dir$meanMSTimeB)
# hist(data.group$meanMisses)
# hist(data.group$meanDockTime)

ggplot(data.ms.group, aes(meanMSTimeB, group=condition, fill=condition)) +
  geom_histogram(bins=30) +
  facet_wrap(~ condition, ncol=2)

ggplot(data.ms.dir, aes(meanMSTimeB, group=direction, fill=direction)) +
  geom_histogram(bins=30) +
  facet_wrap(~ direction, ncol=3)

ggplot(data.group, aes(meanMisses, group=condition, fill=condition)) +
  geom_histogram(bins=30) +
  facet_wrap(~ condition, ncol=2)

ggplot(data.group, aes(meanDockTime, group=condition, fill=condition)) +
  geom_histogram(bins=30) +
  facet_wrap(~ condition, ncol=2)
```

# Docking Time 

## Mode Switching Task

### Chart 

```{r}
kable(dplyr::select(filter(data.stats, task == 'task'), task, methodSwitch, mDT, sdDT))
```

### Graph

```{r  }
ggplot(data=filter(data.stats, task == 'task'), aes(x=interaction(mode, condition), y=mDT, fill=interaction(mode, condition))) +
  geom_bar(stat="identity") +
  geom_errorbar(aes(ymin = clDT, ymax = cuDT), width = 0.2, size = .5, position = position_dodge(.7)) +
  geom_text(aes(label=round(mDT,digits=1)), size = 3, position = position_dodge(0.7), vjust = 3.2) +
  scale_x_discrete(name="Condition") +
  scale_y_continuous(name="Docking Time (ms)") +
  theme(axis.text.x = element_text(angle = 40, vjust = 1, hjust=1),
        legend.position = 'bottom')
```

Docking time was fastest when switching between touch and pen, and slowest when switching between trackpad and mouse.

## Baseline Task

### Chart 

```{r  }
kable(dplyr::select(filter(data.stats, task == 'baseline'), task, condition, mDT, sdDT))
```

### Graph

```{r  }
ggplot(data=filter(data.stats, task == 'baseline'), aes(x=condition, y=mDT, fill=condition)) +
  geom_bar(stat="identity") +
  geom_errorbar(aes(ymin = clDT, ymax = cuDT), width = 0.2, size = .5, position = position_dodge(.7)) +
  geom_text(aes(label=round(mDT,digits=1)), size = 3, position = position_dodge(0.7), vjust = 3.2) +
  scale_x_discrete(name="Condition") +
  scale_y_continuous(name="Docking Time (ms)") +
  theme(axis.text.x = element_text(angle = 40, vjust = 1, hjust=1),
        legend.position = 'bottom')
```

## Effect of  Mode Switching Devices 

### Normality Check

```{r}
m <- aov(meanDockTime ~ condition*block, data=data.group)
pander(normalCheck(m))
```

Data is normally distributed

### Box-Cox Transformation

```{r}
boxcox(meanDockTime ~ condition*block, data=data.group, plotit=T)
```

An effective lambda value is 0.7?

```{r}
datatr = data.group %>%
    mutate(meanDockTime = meanDockTime^(0.8))

m <- aov(meanDockTime ~ condition*block, data=datatr)
pander(normalCheck(m))
```

Nah, it's not working - try the ART instead.

### ANOVAs on ART Data

```{r warning=FALSE, message=FALSE}
a = art(meanDockTime ~ methodSwitch*block + Error(participantNo), data=data.group)
anova(a)
```

### Post-Hoc Comparisons

```{r warning=FALSE, message=FALSE}
b = art.con(a, "methodSwitch") %>% summary() %>% mutate(sig = ifelse(p.value < 0.05, "*", "")) 
b

docking.postHoc = as.data.frame(b) %>% mutate(sig = ifelse(p.value < 0.05, "*", "")) 
```

### ANOVAs & Post-hoc comparisons on ART Data by Device

#### Mouse

```{r warning=FALSE, message=FALSE}
a = art(meanDockTime ~ condition*block + Error(participantNo), data=mouse)
anova(a)
```

```{r warning=FALSE, message=FALSE}
a = art(meanDockTime ~ condition + Error(participantNo), data=mouse)
art.con(a, "condition") %>% summary() %>% mutate(sig = ifelse(p.value < 0.05, "*", ""))
```

#### Touch

```{r warning=FALSE, message=FALSE}
a = art(meanDockTime ~ condition*block + Error(participantNo), data=touch)
anova(a)
```

```{r warning=FALSE, message=FALSE}
a = art(meanDockTime ~ condition + Error(participantNo), data=touch)
art.con(a, "condition") %>% summary() %>% mutate(sig = ifelse(p.value < 0.05, "*", ""))
```

#### Pen

```{r warning=FALSE, message=FALSE}
a = art(meanDockTime ~ condition*block + Error(participantNo), data=pen)
anova(a)
```

```{r warning=FALSE, message=FALSE}
a = art(meanDockTime ~ condition + Error(participantNo), data=pen)
art.con(a, "condition") %>% summary() %>% mutate(sig = ifelse(p.value < 0.05, "*", ""))
```

#### Trackpad

```{r warning=FALSE, message=FALSE}
a = art(meanDockTime ~ condition*block + Error(participantNo), data=trackpad)
anova(a)
```

```{r warning=FALSE, message=FALSE}
a = art(meanDockTime ~ condition + Error(participantNo), data=trackpad)
art.con(a, "condition") %>% summary() %>% mutate(sig = ifelse(p.value < 0.05, "*", ""))
```

# Miss Count

## Mode Switching Task

### Chart

```{r  }
kable(dplyr::select(filter(data.stats, task == 'task'), task, methodSwitch, mMC, sdMC))
```

### Graph

```{r  }
ggplot(data=filter(data.stats, task == 'task'), aes(x=condition, y=mMC, fill=condition)) +
  geom_bar(stat="identity") +
  geom_text(aes(label=round(mMC,digits=2)), size = 3, position = position_dodge(0.7), vjust = 3.2) +
  scale_x_discrete(name="Condition") +
  scale_y_continuous(name="Mean Miss Count") +
  theme(axis.text.x = element_text(angle = 40, vjust = 1, hjust=1),
        legend.position = 'bottom')

# ggplot(data=filter(data.stats.block, task == 'task'), aes(x=interaction(block, condition), y=mMC, fill=condition)) +
#   geom_bar(stat="identity") +
#   geom_text(aes(label=round(mMC,digits=2)), size = 3, position = position_dodge(0.7), vjust = 3.2) +
#   scale_x_discrete(name="Condition") +
#   scale_y_continuous(name="Mean Miss Count") +
#   theme(axis.text.x = element_text(angle = 40, vjust = 1, hjust=1),
#         legend.position = 'bottom')
```

### Percentages

```{r}
mean(data$missCount)
sd(data$missCount)

sum(data$wrongModeCount) / (sum(data$posMissCount) + sum(data$wrongModeCount)) * 100
sum(data$posMissCount) / (sum(data$posMissCount) + sum(data$wrongModeCount)) * 100
```

## Baseline Task

### Chart

```{r  }
kable(dplyr::select(filter(data.stats, task == 'baseline'), task, condition, mMC, sdMC))
```

### Graph

```{r  }
ggplot(data=filter(data.stats, task == 'baseline'), aes(x=condition, y=mMC, fill=condition)) +
  geom_bar(stat="identity") +
  geom_text(aes(label=round(mMC,digits=2)), size = 3, position = position_dodge(0.7), vjust = 3.2) +
  scale_x_discrete(name="Condition") +
  scale_y_continuous(name="Mean Miss Count") +
  theme(axis.text.x = element_text(angle = 40, vjust = 1, hjust=1),
        legend.position = 'bottom')
```

## Effect of Mode Switching Devices 

### Normality Check

```{r}
m <- aov(meanMisses ~ methodSwitch*block, data=data.group)
pander(normalCheck(m))
```

Not normally distributed, need to do transform?

### Box-Cox Transformation

```{r}
#boxcox(meanMisses ~ task*condition*block, data=data.long, plotit=T)
```

Not all values are positive - cannot do Box-Cox transform

```{r}
# datatr = data.long %>%
#     mutate(meanDockTime = meanDockTime^(-0.2))
# 
# m <- aov(meanDockTime ~ task*condition, data=datatr)
# pander(normalCheck(m))
```

### ANOVAs on ART Data

```{r warning=FALSE, message=FALSE}
a = art(meanMisses ~ methodSwitch*block + Error(participantNo), data=data.group)
anova(a)
```

### Post-Hoc Comparisons

```{r warning=FALSE, message=FALSE}
b = art.con(a, "methodSwitch") %>% summary() %>% mutate(sig = ifelse(p.value < 0.05, "*", "")) 
b

mc.postHoc = as.data.frame(b) %>% mutate(sig = ifelse(p.value < 0.05, "*", "")) 
art.con(a, "block") %>% summary() %>% mutate(sig = ifelse(p.value < 0.05, "*", "")) 
```


### ANOVAs & Post-hoc comparisons on ART Data by Device

#### Mouse

```{r warning=FALSE, message=FALSE}
a = art(meanMisses ~ condition*block + Error(participantNo), data=mouse)
anova(a)
```

```{r warning=FALSE, message=FALSE}
a = art(meanMisses ~ condition + Error(participantNo), data=mouse)
art.con(a, "condition") %>% summary() %>% mutate(sig = ifelse(p.value < 0.05, "*", ""))
```

#### Touch

```{r warning=FALSE, message=FALSE}
a = art(meanMisses ~ condition*block + Error(participantNo), data=touch)
anova(a)
```

```{r warning=FALSE, message=FALSE}
a = art(meanMisses ~ condition + Error(participantNo), data=touch)
art.con(a, "condition") %>% summary() %>% mutate(sig = ifelse(p.value < 0.05, "*", ""))
```

#### Pen

```{r warning=FALSE, message=FALSE}
a = art(meanMisses ~ condition*block + Error(participantNo), data=pen)
anova(a)
```

```{r warning=FALSE, message=FALSE}
a = art(meanMisses ~ condition + Error(participantNo), data=pen)
art.con(a, "condition") %>% summary() %>% mutate(sig = ifelse(p.value < 0.05, "*", ""))
```

#### Trackpad

```{r warning=FALSE, message=FALSE}
a = art(meanMisses ~ condition*block + Error(participantNo), data=trackpad)
anova(a)
```

```{r warning=FALSE, message=FALSE}
a = art(meanMisses ~ condition + Error(participantNo), data=trackpad)
art.con(a, "condition") %>% summary() %>% mutate(sig = ifelse(p.value < 0.05, "*", ""))
```

# Switching Miss Count

```{r}
noBaseline = filter(data.ms, data.ms$task != "baseline")
sum(noBaseline$switchMissCount > 0)
sum(noBaseline$wrongModeCount > 0)

info <- noBaseline[noBaseline$switchMissCount > 0,] %>% group_by(direction) %>% summarize(count=n()) 
kable(info)
```

<!-- # Switching Point -->

<!-- ## Mode Switching Task -->

<!-- ### Chart -->

<!-- ```{r  } -->
<!-- kable(dplyr::select(filter(data.ms.stats, task == 'task'), task, condition, mST, sdST)) -->
<!-- ``` -->

<!-- ### Graph -->

<!-- ```{r  } -->
<!-- ggplot(data=filter(data.ms.stats, task == 'task'), aes(x=condition, y=mST, fill=condition)) + -->
<!--   geom_bar(stat="identity") + -->
<!--   geom_errorbar(aes(ymin = clST, ymax = cuST), width = 0.2, size = .5, position = position_dodge(.7)) + -->
<!--   geom_text(aes(label=round(mST,digits=1)), size = 3, position = position_dodge(0.7), vjust = 3.2) + -->
<!--   scale_x_discrete(name="Condition") + -->
<!--   scale_y_continuous(name="Switching Point (ms)") + -->
<!--   theme(axis.text.x = element_text(angle = 40, vjust = 1, hjust=1), -->
<!--         legend.position = 'bottom') -->
<!-- ``` -->

<!-- ## Effect of Task & Mode Switching Devices  -->

<!-- ### Normality Check -->

<!-- ```{r} -->
<!-- m <- aov(meanSwitchTime ~ condition, data=data.ms.long) -->
<!-- pander(normalCheck(m)) -->
<!-- ``` -->

<!-- Data is normally distributed. -->

<!-- <!-- ### Box-Cox Transformation --> -->

<!-- <!-- ```{r} --> -->
<!-- <!-- boxcox(meanSwitchTime ~ task*condition*block, data=data.ms.long, plotit=T) --> -->
<!-- <!-- ``` --> -->

<!-- <!-- An effective lambda value is -0.15? --> -->

<!-- <!-- ```{r} --> -->
<!-- <!-- datatr = data.ms.long %>% --> -->
<!-- <!--     mutate(meanSwitchTime = meanSwitchTime^(-0.15)) --> -->

<!-- <!-- m <- aov(meanSwitchTime ~ task*condition*block, data=datatr) --> -->
<!-- <!-- pander(normalCheck(m)) --> -->
<!-- <!-- ``` --> -->

<!-- ### Repeated measures ANOVA on transformed data -->

<!-- ```{r, warning=FALSE} -->
<!-- anova = ezANOVA(data.ms.long, dv=.(meanSwitchTime), wid=.(participantNo), within=.(condition), detailed=TRUE) -->
<!-- # kable(anova$`Mauchly's Test for Sphericity`) -->
<!-- # kable(anova$`Sphericity Corrections`) -->
<!-- # kable(anova$ANOVA) -->
<!-- anova_apa = anova_apa(anova, sph_corr ="gg", es = "ges", print=FALSE) -->
<!-- input = anova_apa$text[2] -->
<!-- task = anova_apa$text[3] -->
<!-- kable(anova_apa) -->
<!-- ``` -->

<!-- Can't run ezANOVA using "task" as a within subjects variable for... reasons? (R complains about it) -->

<!-- ## Mode Switching Task by Direction -->

<!-- ### Chart -->

<!-- ```{r message=FALSE} -->
<!-- kable(dplyr::select(filter(data.ms.stats.direction, task == 'task'), direction, mST, sdST)) -->
<!-- ``` -->

<!-- ### Graph -->

<!-- ```{r  } -->
<!-- ggplot(data=filter(data.ms.stats.direction, task == 'task'), aes(x=direction, y=mST, fill=direction)) + -->
<!--   geom_bar(stat="identity") + -->
<!--   geom_errorbar(aes(ymin = clST, ymax = cuST), width = 0.2, size = .5, position = position_dodge(.7)) + -->
<!--   geom_text(aes(label=round(mST,digits=1)), size = 3, position = position_dodge(0.7), vjust = 3.2) + -->
<!--   scale_x_discrete(name="Condition") + -->
<!--   scale_y_continuous(name="Switching Point (ms)") + -->
<!--   theme(axis.text.x = element_text(angle = 40, vjust = 1, hjust=1), -->
<!--         legend.position = 'bottom') -->
<!-- ``` -->

<!-- ## Baseline Task -->

<!-- ### Chart -->

<!-- ```{r  } -->
<!-- kable(dplyr::select(filter(data.ms.stats.bl, task == 'baseline'), task, condition, mST, sdST)) -->
<!-- ``` -->

<!-- ### Graph -->

<!-- ```{r  } -->
<!-- ggplot(data=filter(data.ms.stats.bl, task == 'baseline'), aes(x=condition, y=mST, fill=condition)) + -->
<!--   geom_bar(stat="identity") + -->
<!--   geom_errorbar(aes(ymin = clST, ymax = cuST), width = 0.2, size = .5, position = position_dodge(.7)) + -->
<!--   geom_text(aes(label=round(mST,digits=1)), size = 3, position = position_dodge(0.7), vjust = 3.2) + -->
<!--   scale_x_discrete(name="Condition") + -->
<!--   scale_y_continuous(name="Switching Time (ms)") + -->
<!--   theme(axis.text.x = element_text(angle = 40, vjust = 1, hjust=1), -->
<!--         legend.position = 'bottom') -->
<!-- ``` -->

# Mode Switching Time 

## Mode Switching Task

### Chart

```{r  }
kable(dplyr::select(filter(data.ms.stats.block, task == 'task'), task, condition, mMTB, sdMTB))
```

### Graph

```{r}
ggplot(data=filter(data.ms.stats, task == 'task'), aes(x=condition, y=mMTB, fill=condition)) +
  geom_bar(stat="identity") +
  geom_errorbar(aes(ymin = clMTB, ymax = cuMTB), width = 0.2, size = .5, position = position_dodge(.7)) +
  geom_text(aes(label=round(mMTB,digits=1)), size = 3, position = position_dodge(0.7), vjust = 3.5) +
  scale_x_discrete(name="Condition") +
  scale_y_continuous(name="Switching Time (ms)") +
  theme(axis.text.x = element_text(angle = 40, vjust = 1, hjust=1),
        legend.position = 'bottom')

ggplot(data=filter(data.ms.stats.block, task == 'task'), aes(x=interaction(block, condition), y=mMTB, fill=condition)) +
  geom_bar(stat="identity") +
  geom_errorbar(aes(ymin = clMTB, ymax = cuMTB), width = 0.2, size = .5, position = position_dodge(.7)) +
  geom_text(aes(label=round(mMTB,digits=1)), size = 3, position = position_dodge(0.7), vjust = 3.2) +
  scale_x_discrete(name="Condition") +
  scale_y_continuous(name="Mode Switching Time (ms)") +
  theme(axis.text.x = element_text(angle = 40, vjust = 1, hjust=1),
        legend.position = 'bottom')
```

## Effect of Task & Mode Switching Devices 

### Normality Check

```{r}
m <- aov(meanMSTimeB ~ condition*block, data=filter(data.ms.group, task == 'task'))
pander(normalCheck(m))
```

Cannot run Box-Cox with negative values.

### ANOVAs on ART Data

```{r warning=FALSE, message=FALSE}
a = art(meanMSTimeB ~ condition*block + Error(participantNo), data=data.ms.group)
anova(a)
```


## Mode Switching Task by Direction

### Chart

```{r message=FALSE}
kable(dplyr::select(filter(data.ms.stats.direction, task == 'task'), task, condition, direction, mMTB, sdMTB))

kable(dplyr::select(filter(data.ms.stats.direction.block, task == 'task'), task, condition, direction, block, mMTB, sdMTB))
```

### Graph

```{r warning=FALSE, message=FALSE }
ggplot(data=filter(data.ms.stats.direction, task == 'task'), aes(x=direction, y=mMTB, fill=direction)) +
  geom_bar(stat="identity") +
  geom_errorbar(aes(ymin = clMTB, ymax = cuMTB), width = 0.2, size = .5, position = position_dodge(.7)) +
  geom_text(aes(label=round(mMTB,digits=1)), size = 3, position = position_dodge(0.7), vjust = 3.2) +
  scale_x_discrete(name="Condition") +
  scale_y_continuous(name="Mode Switching Time (ms)") +
  theme(axis.text.x = element_text(angle = 40, vjust = 1, hjust=1),
        legend.position = 'bottom')

# ggplot(data=filter(data.ms.stats.direction.block, task == 'task'), aes(x=interaction(block, direction), y=mMTB, fill=direction)) +
#   geom_bar(stat="identity") +
#   geom_errorbar(aes(ymin = clMTB, ymax = cuMTB), width = 0.2, size = .5, position = position_dodge(.7)) +
#   geom_text(aes(label=round(mMTB,digits=1)), size = 3, position = position_dodge(0.7), vjust = 3.2) +
#   scale_x_discrete(name="Condition") +
#   scale_y_continuous(name="Mode Switching Time (ms)") +
#   theme(axis.text.x = element_text(angle = 40, vjust = 1, hjust=1),
#         legend.position = 'bottom')
```

## Effect of Task & Mode Switching Devices 

### Normality Check

```{r}
m <- aov(meanMSTimeB ~ block*direction, data=filter(data.ms.dir, task == 'task'))
pander(normalCheck(m))
```

Can't run Box-Cox due to negative mode switching times.

### ANOVAs on ART Data

```{r warning=FALSE, message=FALSE}
a = art(meanMSTimeB ~ direction*block + Error(participantNo), data=filter(data.ms.dir, task == 'task'))
anova(a)
```

### Post-Hoc Comparisons

```{r warning=FALSE, message=FALSE}
b = art.con(a, "direction") %>% summary() %>% mutate(sig = ifelse(p.value < 0.05, "*", "")) 
b
c = as.data.frame(b) %>% mutate(sig = ifelse(p.value < 0.05, "*", "")) 
art.con(a, "block") %>% summary() %>% mutate(sig = ifelse(p.value < 0.05, "*", "")) 
```

## Location

### Chart

```{r message=FALSE}
kable(dplyr::select(filter(data.ms.stats.loc, task == 'task'), task, condition, location, mMTB, sdMTB))

```

### Graph

```{r warning=FALSE, message=FALSE }
ggplot(data=filter(data.ms.stats.loc, task == 'task'), aes(x=condition, y=mMTB, fill=location)) +
  geom_bar(stat="identity", position = position_dodge()) +
  geom_errorbar(aes(ymin = clMTB, ymax = cuMTB), width = 0.2, size = .5, position = position_dodge(0.9)) +
  geom_text(aes(label=round(mMTB,digits=1)), size = 3, position = position_dodge(0.9), vjust = 3.2) +
  scale_x_discrete(name="Location") +
  scale_y_continuous(name="Mode Switching Time (ms)") +
  theme(axis.text.x = element_text(angle = 40, vjust = 1, hjust=1),
        legend.position = 'bottom')

ggplot(data=filter(data.ms.stats.loc2, task == 'task'), aes(x=location, y=mMTB, fill=location)) +
  geom_bar(stat="identity", position = position_dodge()) +
  geom_errorbar(aes(ymin = clMTB, ymax = cuMTB), width = 0.2, size = .5, position = position_dodge(0.9)) +
  geom_text(aes(label=round(mMTB,digits=1)), size = 3, position = position_dodge(0.9), vjust = 3.2) +
  scale_x_discrete(name="Location") +
  scale_y_continuous(name="Mode Switching Time (ms)") +
  theme(axis.text.x = element_text(angle = 40, vjust = 1, hjust=1),
        legend.position = 'bottom')
```

## Effect of Task & Mode Switching Devices 

### Normality Check

```{r}
m <- aov(meanMSTimeB ~ block*condition*location, data=filter(data.ms.loc, task == 'task'))
pander(normalCheck(m))

m <- aov(meanMSTimeB ~ block*location, data=filter(data.ms.loc, task == 'task'))
pander(normalCheck(m))
```

Can't run Box-Cox due to negative mode switching times.

### ANOVAs on ART Data

```{r warning=FALSE, message=FALSE}
a = art(meanMSTimeB ~ condition*location*block + Error(participantNo), data=filter(data.ms.loc, task == 'task'))
anova(a)

a = art(meanMSTimeB ~ location*block + Error(participantNo), data=filter(data.ms.loc, task == 'task'))
anova(a)
```

### Post-Hoc Comparisons

```{r warning=FALSE, message=FALSE}
art.con(a, "location") %>% summary() %>% mutate(sig = ifelse(p.value < 0.05, "*", "")) 
```
